Final Model Analysis

### 2017-08-31 model fitting/final_model.Rmd
reorganized code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
x <- read.csv("final_data.csv", head = TRUE)
library(survival); library(dplyr); library(rms)
```

@@

```{r, echo = FALSE}
# building model on train1 (df set to 5 for all splines at first, but setting tag and newline to 4 minimized AIC and performed best)
trainmodel <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = train1, x = TRUE, y = TRUE)
AIC(trainmodel, k = 2) # 54421.53
trainmodel
```

@@

```{r, functions for cv, echo = FALSE}
# function to perform cross validation, vars should be string: "new_category + new_user..."
crossval <- function(vars, train, test) {
  formula <- paste("Surv(time_until_answer, answered) ~ ", vars, sep = "")
  model <- rms::cph(as.formula(formula), data = train)

@@

```{r, echo = FALSE}
dd = datadist(x)
options(datadist = "dd")

x$text_length2 <- x$text_length**2 # for future use
x$sqrt_tag_score <- sqrt(x$avg_tag_score)

final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE, time.inc = 0.5, dxy = TRUE)
final

@@

```{r, not using these functions}
# not using these functions
# function to delete overly influential questions (used in function below)
delete_influential <- function(var) {
  thresh <- mean(score[[var]]) + (sd(score[[var]]) * 30)
  delete <- which(abs(score[[var]]) > thresh)
  return(delete)
}

@@

metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
AIC(metric, k = 2) # 83023

@@

# either specify newdata, linear.predictors or x
# number on the rows of the surv matrix is the index 
# function is very slow if full data set is used
rms::survest(final, newdata = test1[1:3,], times = c(0.5, 1, 10), conf.int = FALSE)

@@

```{r}
# plots log hazard for individual predictors 
ggplot(Predict(final, new_category))  
ggplot(Predict(final, device_length))
ggplot(Predict(final, text_length))
ggplot(Predict(final, avg_tag_length))
ggplot(Predict(final, newline_ratio))

times <- sort(unique(x$time_until_answer))
pec::plotPredictSurvProb(final, newdata = x[1:4,], times = times) # ugly output

# must specify a variable 
rms::survplot(final, ampm, time.inc = 100, col = 1:4, n.risk = TRUE, xlab = "Hours")
rms::survplot(final, new_category, time.inc = 100, col = 1:length(levels(x$new_category)), xlab = "hour")
rms::survplot(final, new_user = 0, conf.int = .95, time.inc = 100) # can change variable it plots 
```

##### Function to output survival probabilities

* input data set with any combination of predictors + times to predict on 
* output corresponding survival probabilities

```{r}
# input vector of times to predict on + data set to be used in predictions
# function runs really slow
# outputs matrix of predicted survival probabilities 
# sets up variables needed in the new data 
get_survival <- function(times, data) {
  # setting up necessary variables in new data 
  newdata <- oshitar::variable_setup(data)
  # imports data to build model on 
  x <- read.csv("final_data.csv", head = TRUE)
  # builds model 
  model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE)
  # gets survival probabilities 
  surv_probs <- pec::predictSurvProb(model, newdata = newdata, times)
  return(surv_probs)
}

get_survival(times = c(0.5, 1, 10), data = out[1:10,])
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
x <- oshitar::variable_setup(out)

library(survival); library(dplyr); library(rms)
```

@@

```{r, echo = FALSE}
# build model on train1 (df set to 5 for all splines at first, but setting tag and newline to 4 minimized AIC and performed best)

trainmodel <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = train1, x = TRUE, y = TRUE)
AIC(trainmodel, k = 2) # 54421.88
trainmodel
```

@@

```{r, functions for cv, include = FALSE}
# function to perform cross validation, vars should be string: "new_category + new_user..."
crossval <- function(vars, train, test) {
  formula <- paste("Surv(time_until_answer, answered) ~ ", vars, sep = "")
  model <- rms::cph(as.formula(formula), data = train)

@@

```{r, echo = FALSE}
dd <- datadist(x)
options(datadist = "dd")
final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                               contain_unanswered + contain_answered + title_questionmark + 
                               title_beginwh + text_contain_punct + text_all_lower + update + 
                               greeting + gratitude + prior_effort + weekday + strat(ampm) + 
                               sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + 
                               rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
                             data = x, x = TRUE, 
                             y = TRUE, surv = TRUE)
final
AIC(final, k = 2) # 69945.32

@@

```{r, not using these functions, include = FALSE}
# not using these functions
# function to delete overly influential questions (used in function below)
delete_influential <- function(var) {
  thresh <- mean(score[[var]]) + (sd(score[[var]]) * 30)
  delete <- which(abs(score[[var]]) > thresh)
  return(delete)
}

@@

metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
AIC(metric, k = 2) # 83125.55

@@

# either specify newdata, linear.predictors or x
# number on the rows of the surv matrix is the index 
# function is very slow if full data set is used
rms::survest(final, newdata = test1[1:3,], times = c(0.5, 1, 10), conf.int = FALSE)
rms::survest(final, times = c(0.5, 1, 10), conf.int = FALSE)

@@

```{r}
# plots log hazard for individual predictors 
dd = datadist(x)
options(datadist="dd")

ggplot(Predict(final, new_category))  
ggplot(Predict(final, device_length))
ggplot(Predict(final, text_length))
ggplot(Predict(final, avg_tag_length))
ggplot(Predict(final, newline_ratio))

times <- sort(unique(x$time_until_answer))
pec::plotPredictSurvProb(final, newdata = x[1:4,], times = c(1, 10, 12, 13, 14)) # ugly output

# must specify a variable 
rms::survplot(final, ampm, time.inc = 100, col = 1:4, n.risk = TRUE, xlab = "Hours")
rms::survplot(final, new_category, time.inc = 100, col = 1:length(levels(x$new_category)), xlab = "hour", label.curves=list(keys=1:length(levels(x$new_category))))
rms::survplot(final, new_user = 0, conf.int = .95, time.inc = 100) # can change variable it plots 
```
